Children's Books:

### 2024-11-30 paper/paper.qmd
final typo checks

---
title: "Children's Books"
subtitle: "What factors influence the likelihood of a book being high-rated?"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (Cookson 2020). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on the likelihood of a book being high-rated. The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
format:
  pdf:
    fig.pos: "H"
toc: true
number-sections: true
bibliography: references.bib
---

@@

The logistic Bayesian logistic regression model revealed that book covers significantly influenced the likelihood of a book being rated highly, with the `Kindle Edition` format standing out as particularly impactful. These findings have practical implications for the publishing industry, offering valuable insights for authors and publishers to explore innovative ways to enhance reader engagement and elevate the literary experience.

@@

The estimand of this paper is the probability that a children's book is "highly-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics. It is difficult to measure the exact number as there are millions of children's books that are published and there could be variations in ratings across countries. Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset [@citedata].

@@

Data analysis is performed using Statistical Programming Language R [@citeR] , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales] and `testthat` [@testthat]. The code involved in the analysis was styled using `lintr` [@citelintr] and `styler` [@citestyler].

@@

@tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high-rated" had more pages on average than "low-rated books". Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2002 and 2000 for the "low-rated" and "high-rated" books respectively. "High-rated" books also received far more ratings on average at 9,5092 ratings, more than four times that of "low-rated" books at an average of 2002 reviews per book. Lastly, `Kindle Edition` covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books). These variables are key in the analysis, and are further mentioned in @sec-data.

@@

@fig-page-count shows that "high-rated" books have more page count than "low-rated" books. Highly-rated books had an average page count of 70.3, compared to the 66.9 average page count of low-rated books.

@@

This study employed a Bayesian logistic regression model to analyze the relationship between children book's `rated_high`` status and the characteristic of the book. The model is as follows:

@@

We used a posterior predictive check in @fig-distribution to evaluate how well the model fits the data. This compares the observed data `y` against the replicated data \mbox{y$_i$} which was generated by our model in @sec-model. The posterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.

@@

@fig-trace and @fig-rhat are the trace plot of the model and Rhat plot of the model respectively. The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model. Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 [@citealexander]

>>>>

---
title: "Children's Books:"
subtitle: "What factors influence the likelihood of a book being high-rated?"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (Cookson 2020). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on the likelihood of a book being high-rated. The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
format:
  pdf:
    fig.pos: "H"
toc: true
number-sections: true
bibliography: references.bib
---

@@

The Bayesian logistic regression model revealed that book covers significantly influenced the likelihood of a book being high-rated, with the `Kindle Edition` format standing out as particularly impactful. These findings have practical implications for the publishing industry, offering valuable insights for authors and publishers to explore innovative ways to enhance reader engagement and elevate the literary experience.

@@

The estimand of this paper is the probability that a children's book is "high-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics. It is difficult to measure the exact number as there are millions of children's books that are published and there could be variations in ratings across countries. Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset [@citedata].

@@

Data analysis is performed using Statistical Programming Language R [@citeR], along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales] and `testthat` [@citetestthat]. The code involved in the analysis was styled using `lintr` [@citelintr] and `styler` [@citestyler].

@@

@tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high-rated" had more pages on average than "low-rated" books. Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2002 and 2000 for the "low-rated" and "high-rated" books respectively. "High-rated" books also received far more ratings on average at 9,592 ratings, more than four times that of "low-rated" books at an average of 2002 reviews per book. Lastly, `Kindle Edition` covers had the highest proportion of "high-rated" books out of any other cover types (as well as low-rated books). These variables are key in the analysis, and are further mentioned in @sec-data.

@@

@fig-page-count shows that "high-rated" books have more page count than "low-rated" books. High-rated books had an average page count of 70.3, compared to the 66.9 average page count of low-rated books.

@@

This study employed a Bayesian logistic regression model to analyze the relationship between children book's `rated_high` status and the characteristic of the book. The model is as follows:

@@

We used a posterior predictive check in @fig-distribution to evaluate how well the model fits the data. This compares the observed data `y` against the replicated data \mbox{y$_rep$} which was generated by our model in @sec-model. The posterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.

@@

@fig-trace and @fig-rhat are the trace plot of the model and Rhat plot of the model respectively. The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model. Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 [@citealexander].
